Large-scale harmonic patterns clustering

### 2010-03-20 Paper/Paper.tex
stuff added back from draft
improved

\subsection{USPOP}

\subsection{Artist Set}

@@

\subsection{Artist Recognition}
Let us be clear, the clustering method proposed in this work is not
intended to perform well at artist recognition. An obvious fact is that
we lose all timbral information which would be usefull. However, we can
imagine that some artist use more often some patterns than others.
See Figure \ref{fig:conf_mat}.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.4\columnwidth]{metallica_pattern}
\end{center}
\caption{\small{Most typical pattern for Metallica.}}
\label{fig:metallica}
\end{figure}

>>>>

\subsection{Cowbell Dataset}
We have $43,300$ songs, giving  $3,720,091$ non zero bars, a bar usually 
contains $4$ beats. WHERE DOES THIS DATA COMES FROM? GIFT FROM EN?

\subsection{USPOP}
We had acces to a low quality (32kbps) version of the songs in the uspop 2002 
data set \cite{uspop2002}.
This well-known data show a great diversity of pop songs, but is not particular
otherwise. We also tried to use Tzanetakis dataset \cite{Tzanetakis2002a}, but 
the $30$ seconds segments seemed hard to analyze by the Echo Nest API, most did
not contain any bar.

uspop2002 serves as testing set to measure how well a codebook learned on
the Cowbell data set can represent new songs. We get Echo Nest features
for $8651$ songs from that dataset.

\subsection{Artist Set}
A set of songs from $20$ artists.

@@

\subsection{Artist Recognition}
Let us be clear, the clustering method proposed in this work is not
intended to perform well at artist recognition. An obvious fact is that
we lose all timbral information which would be usefull. However, we can
imagine that some artist use more often some patterns than others.
Best accuracy reported is around $54.5\%$. Our result is $23.4\%$. Random
is around $5\%$.

See Figure \ref{fig:conf_mat}.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.4\columnwidth]{metallica_pattern}
\end{center}
\caption{\small{Most typical pattern for Metallica.
COULD BE MIXED WITH TORI AMOS FIGURE.
}}
\label{fig:metallica}
\end{figure}
